Holomorphic field theories and higher algebra

### 2023-08-18 highervertexops.tex
rearranged things and added place for me to insert some ideas

We emphasize that this decomposition does \textit{not} respect the commutative product.

@@

@@

In the single-variable case, the residue map defines an identification
\beqn
\C((z)) \simeq \Omega^1 (\Hat{D})^\vee = \left(\C((z)) \d z\right)^\vee
\eeqn
where the right hand side is the continuous linear dual.
Explicitly, this identification takes a Laurent series $f$ to the functional 
\beqn
g \d z \mapsto \op{Res}_{1d} (f g \d z) .
\eeqn

@@

\subsection{Distributions on punctured affine space}

The model $\sfA$ for algebraic functions on punctured affine space was constructed using the ring
\beqn
\sfR = \C[z_i,\lambda_i] \slash (\sum_i z_i \lambda_i = 1) .
\eeqn
Let $\Hat{\sfR}$ denote the completion of this ring with respect to the ideal generated by $z_1,z_2$.
So I think
\beqn
\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (\sum_i z_i \lambda_i) .
\eeqn

Let $\Hat{\sfA}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
The cohomology of $(\Hat\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.

@@

>>>>

We emphasize that this decomposition does \textit{not} respect the commutative product.
\owen{I'm confused what you mean here. Can you spell out what you mean in more detail?}

@@

\subsection{Functions on punctured formal disk}

The model $\sfA$ for algebraic functions on punctured affine space was constructed using the ring
\beqn
\sfR = \C[z_i,\lambda_i] \slash (\sum_i z_i \lambda_i = 1) .
\eeqn
Let $\Hat{\sfR}$ denote the completion of this ring with respect to the ideal generated by~$z_1,z_2$:
\beqn
\Hat{\sfR} = \C[[z_i]][\lambda_i] \slash (\sum_i z_i \lambda_i) .
\eeqn
\owen{As you said originally, this second line takes the completion for the $z$s first and then adjoins the $\lambda$s, while your definition involves completing after adjoining the $\lambda$s. It's not clear those operations commute.}

Let $\Hat{\sfA}$ be the graded algebra free generated over $\Hat{\sfR}$ and the degree one variable $\omega$.
The cohomology of $(\Hat\sfA, \dbar)$ is $\C[[z_i]]$ in degree zero and $\C[\lambda_i]$ in degree one.
\owen{We need to be really careful about this, and it probably depends on what category of vector spaces (e.g., complete filtered?) we work in. The $SL(2)$-approach above manifestly breaks down, although it gives us useful information.}

@@

In the single-variable case, the residue map defines an identification
\beqn
\C((z)) \simeq \Omega^1 (\Hat{D})^\vee = \left(\C((z)) \d z\right)^\vee
\eeqn
where the right hand side is the continuous linear dual.
Explicitly, this identification takes a Laurent series $f$ to the functional 
\beqn
g \, \d z \mapsto \op{Res}_{1d} (f g \d z) .
\eeqn
In this way, distributions and functions on the punctured formal disk are isomorphic.

@@

@@

\section{Recollections on one-dimensional algebraic free field realization}
